Reasoning about a Capability Machine with Local Capabilities

### 2017-06-14 popl-2018/paper.tex
added adversary unknown piece of code

\section{Stack and return pointer management using local capabilities}
\label{sec:stack-and-return-pointer}
One of the contributions in this paper is a demonstration that local
capabilities on a capability machine support a calling convention that enforces
control-flow correctness in a way that is provably watertight, potentially
efficient, does not rely on a trusted central stack manager, and supports
higher-order interfaces to an adversary. In this section, we explain this
convention's high-level approach, the security measures to be taken in a number
of situations (motivating each separately with a summary table at the end).
After that, we define a number of reusable macro-instructions that can be used
to conveniently apply the proposed convention in subsequent examples.

>>>>

\section{Stack and return pointer management using local capabilities}
\label{sec:stack-and-return-pointer}
One of the contributions in this paper is a demonstration that local
capabilities on a capability machine support a calling convention that enforces
control-flow correctness in a way that is provably watertight, potentially
efficient, does not rely on a trusted central stack manager, and supports
higher-order interfaces to an adversary where an adversary is just some unknown piece of code. In this section, we explain this
convention's high-level approach, the security measures to be taken in a number
of situations (motivating each separately with a summary table at the end).
After that, we define a number of reusable macro-instructions that can be used
to conveniently apply the proposed convention in subsequent examples.
